Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-11 article-counts-per-year-figure.Rmd
redid figure with pub counts

```{r}
dat %>%
  tidyr::pivot_longer(!year) %>%
  ggplot2::ggplot(ggplot2::aes(x = year, y = value, colour = name)) + ggplot2::geom_point()
ggplot2::ggsave("figures/mr-gwas-counts-scatter.png")
```

>>>>

```{r}
dat %>%
  tidyr::pivot_longer(!year) %>%
  dplyr::filter(year != 2022) %>%
  ggplot2::ggplot(ggplot2::aes(x = year, y = value, fill = name)) + 
  ggplot2::geom_bar(stat = "identity", 
                    position=ggplot2::position_dodge()) + 
  ggplot2::scale_fill_manual(labels = c("GWAS", "MR"), values=c('#999999','#E69F00')) + 
  ggplot2::ylab("Annual publication count") + 
  ggplot2::xlab("Year") + 
  ggplot2::guides(fill = ggplot2::guide_legend("Search terms"))

ggplot2::ggsave("figures/mr-gwas-counts.png")
```

### 2022-02-11 mr-review.Rmd
redid figure with pub counts

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r, article-counts, fig.cap= "Upward trend in article counts by year for keyword searches: 1. mendelian randomization and 2. genome-wide association study."}
knitr::include_graphics("figures/mr-gwas-counts-scatter.png")
```

@@

```{r, dag1, fig.cap = "Scenario where the genetic variant G affects an intermediate variable W on the pathway to the exposure X. This violates the exclusion restriction assumption."}
g1 <- dagitty::dagitty( "dag {
	G -> W -> X -> Y
	W -> Y
}")
plot(dagitty::graphLayout(g1))
```

@@

## Statistical models and methods for MR with multiple instruments and one outcome

@@

@@

# Non-continuous outcomes

>>>>

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
```

@@

```{r, article-counts, fig.cap= "Upward trend in article counts by year for keyword searches: 1. mendelian randomization and 2. genome-wide association study."}
knitr::include_graphics("figures/mr-gwas-counts.png")
```

@@

```{r, dag1, fig.cap = "Scenario where the genetic variant G affects an intermediate variable W on the pathway to the exposure X. This violates the exclusion restriction assumption."}

```

@@

## Statistical models and methods for MR with multiple instruments and one continuous outcome

@@

# Binary, Count, and Time-to-event outcomes

@@
